{{< var titll >}}

### 2024-07-08 index.qmd
headlines

---
title: "Manifold Destiny - or how to rig an election"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

>>>>

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

### 2024-07-08 paper.qmd
abc
templated
headlines

---
title: ""
abstract: "Abstract goes here"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

```{r}
knitr::knit_exit()
```

>>>>

---
title: "{{< var titll >}}"
abstract: "Abstract goes here"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

# {{< var sec1.nmn >}}
## {{< var sec1.un1 >}}
## {{< var sec1.un2 >}}
## {{< var sec1.un3 >}}
## {{< var sec1.un4 >}}
## {{< var sec1.un5 >}}
## {{< var sec1.un6 >}}
## {{< var sec1.un7 >}}

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
## {{< var sec2.un2 >}}
## {{< var sec2.un3 >}}
## {{< var sec2.un4 >}}
## {{< var sec2.un4 >}}

# {{< var sec3.nmn >}}
## {{< var sec3.un1 >}}
## {{< var sec3.un2 >}}

# {{< var sec5.nmn >}}

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}
## {{< var sec6.un4 >}}

# {{< var sec7.nmn >}}
## {{< var sec7.un1 >}}

# {{< var sec8.nmn >}}

```{r,echo=F}
knitr::knit_exit()
```

### 2024-07-08 presentation.qmd
headlines

```{r, echo=F, message=F, warning=F, results='hide'}
library(huxtable)
library(kableExtra)
#Sys.info()[['sysname']]=="Emscripten"
#ManifoldDestiny::wasmconload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```

@@

# {{< var sec2.nmn >}}
# {{< var sec3.nmn >}}
# {{< var sec4.nmn >}}
# {{< var sec5.nmn >}}
# {{< var sec6.nmn >}}
# {{< var sec7.nmn >}}
# {{< var sec8.nmn >}}
# {{< var sec9.nmn >}}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
library(huxtable)
library(kableExtra)
#Sys.info()[['sysname']]=="Emscripten"
#ManifoldDestiny::wasmconload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/r/simulations.r'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```

@@

# {{< var sec1.nmn >}}
## {{< var sec1.un1 >}}
## {{< var sec1.un2 >}}
## {{< var sec1.un3 >}}
## {{< var sec1.un4 >}}
## {{< var sec1.un5 >}}
## {{< var sec1.un6 >}}
## {{< var sec1.un7 >}}

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
## {{< var sec2.un2 >}}
## {{< var sec2.un3 >}}
## {{< var sec2.un4 >}}
## {{< var sec2.un4 >}}

# {{< var sec3.nmn >}}
## {{< var sec3.un1 >}}
## {{< var sec3.un2 >}}

# {{< var sec5.nmn >}}

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

# {{< var sec7.nmn >}}
## {{< var sec7.un1 >}}

# {{< var sec8.nmn >}}

# {{< var sec9.nmn >}}
